---
output: 
  pdf_document:
    number_sections: true
urlcolor: black
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\begin{center}
   \framebox{
      \vbox{\vspace{2mm}
    \hbox to 6.28in { {\bf STA 106B: Applied Statistical Methods - Analysis of Variance
		\hfill Spring 2024} }
       \vspace{4mm}
       \hbox to 6.28in { {\Large \hfill Discussion 1  \hfill} }
       \vspace{2mm}
       \hbox to 6.28in { {\it \hfill TA: Zach Quan, zkquan@ucdavis.edu \hfill} }
       \vspace{1mm}
       \hbox to 6.28in { {\it \hfill \href{https://ucdavis.zoom.us/j/2478285521}{Office Hour: Thursday 5:00 pm - 7:00 pm} \hfill} }
        \vspace{1mm}
       \hbox to 6.28in { {\it \hfill {Zoom Link: https://ucdavis.zoom.us/j/2478285521} \hfill} }
       }
   }
\end{center}

\vspace*{4mm}


# Discussion
The discussion section will provide additional help on \textbf{data analysis (in R)}, \textbf{concept understanding}, and \textbf{homework assignments/quizzes}. Discussion notes will be uploaded to the Home page on Canvas weekly.

# Setting Up R
## Installing R
One of the wonderful things about $R$ is that it is free. This way, you may work on your homework in the comfort of your home. To download and install R, complete the following steps:
\begin{enumerate}
	\item Go to \url{http://cran.freestatistics.org/}
	\item If you have Linux, click "Download R for Linux" and select the appropriate platform.
	\item If you have a Mac, click "Download R for (Mac) OS X", and select the appropriate package based on your operating system.
	\item Follow the instructions of the installer.
\end{enumerate}
Congratulations, you have now (hopefully) installed R.

## Installing RStudio
To install RStudio, complete the following steps:
\begin{enumerate}
	\item Go to \href{http://rstudio.org/}{http://rstudio.org/}
	\item Click on the "Download RStudio" button.
	\item Select the "Desktop" option.
	\item Select the appropriate link (usually the recommended one for your system works just fine).
\end{enumerate}

\newpage
## Installing R Markdown packages
- Install Markdown package by typing this command in R Console:
```{r, eval=FALSE}
install.packages('rmarkdown')
```
- Install LaTeX (TinyTeX) for PDF reports by typing this command in R Console:
```{r, eval=FALSE}
install.packages ('tinytex')
```
- Once the installation has been completed, type
```{r, eval=FALSE}
tinytex::install_tinytex()
```


# Brief introduction to Rstudio and R Markdown

## Rstudio
\begin{itemize}
	\item Click the RStudio icon to run this program, and R will open automatically in the background at the same time. You should have 4 panels. A brief description of the four windows follows:
	\begin{enumerate}
		\item \textbf{Environment, History}: This window lists all Variables, Data, and Functions defined by us.
		\item \textbf{Files, Plots, Packages, Help}: We can use the help or \text{?} command to get the documentation of any functions, and the relevant help document will be opened. Furthermore, if we plot a figure, it will be displayed in this panel as well.
		\item \textbf{Console}: The place we can type in commands and retrieve our output.
		\item \textbf{Source}: The place to store our commands.
	\end{enumerate}
	\item Ways of typing commands in R:
	\begin{enumerate}
		\item Type code in Console
		\item \textbf{Recommended}: Create a new source file, type code in the file: \\
		click the green cross (+) in the top left corner, and choose "R script".
	\end{enumerate}
	\item Running R code:
	\begin{enumerate}
		\item In R Console: hit *Enter* after the command line
		\item In R Source files:\\
		 Place the cursor in the line or highlight the part you want to run and hit the "run" button on the menu, or apply the shortcut: \textbf{command + Return(MAC)} or \textbf{Ctrl + Enter(Windows)}
	\end{enumerate}
	\item Save R Source files (Script, notebook, markdown):
	\begin{enumerate}
		\item click the blue square button in the source window.
		\item click File $>$ Save/ Save as.
	\end{enumerate}
\end{itemize}


## R Markdown

- Create an R markdown file:
    1. Click the green "+" in the top left in Rstudio > R markdown > write a title and choose output file format > OK
    2. Type text in the white space for your report
    3. Write R code in the grey R chunk, which can be created by typing ` ```{r} ` at the begining and ` ``` ` at the end.
    4. Click the **Knit** button to generate your pdf/html file by R Markdown file.
    
- More details about R Markdown: \url{https://rmarkdown.rstudio.com/authoring_basics.html}

- An R Markdown Cookbook: \url{https://bookdown.org/yihui/rmarkdown-cookbook/}

